Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-01-31 scagnostics.Rmd
Comments Rory.
Acknowledgments added.
Affiliation showing.

authors: 
- name: Ursula Laa
  thanks: The authors gratefully acknowledge the support of the Australian Research Council
  affiliation: Department of Physics, Monash University
  email: ursula.laa@monash.edu

- name: Dianne Cook
  affiliation: Department of Econometrics and Business Statistics, Monash University

@@

The first example contains 2538 posterior samples obtained by fitting source parameters to the observed gravitational wave signal GW170817 from a neutron star merger [@PhysRevLett119161101]. Data has been downloaded from @ligoData. The fitting procedures are described in detail in @Abbott2018exr. There are six parameters of physical interest (6-D) with some known relationships. Projection pursuit is used to find the known relationships.

@@

>>>>

authors: 
- name: Ursula Laa
  address: School of Physics and Astronomy, Monash University
  email: ursula.laa@monash.edu
- name: Dianne Cook
  address: Department of Econometrics and Business Statistics, Monash University
  email: dicook@monash.edu

@@

The first example contains 2538 posterior samples obtained by fitting source parameters to the observed gravitational wave signal GW170817 from a neutron star merger [@PhysRevLett119161101]. Data has been downloaded from @ligoData. The fitting procedures are described in detail in @Abbott2018exr. We consider six parameters of physical interest (6-D) with some known relationships. Projection pursuit is used to find the known relationships.

@@

# Acknowledgments {-}
We thank Rory Smith for help with the gravitational wave examples, and German Valencia for useful comments.
